Walmart
========================================================

This is Twitter sentiment analysis for Walmart.
```{r message=FALSE}
library("twitteR")
library("wordcloud")
library("tm")
library("ggplot2")
library("reshape2")
```
Following code was executed & evaluated for five consecutive open market days from December 1st to December 3rd 2014 for twitter Walmart.
```{r eval=FALSE}
my.key <-"1PE8eCeguQTdpiPl6oyiUDx6K"
my.secret <-"DTEQfmrba0kaKB7IphzQACtwpWhh9pAS7qdH2SUilurnW69ZZb"

cred <- OAuthFactory$new(consumerKey=my.key,
                         consumerSecret=my.secret,
                         requestURL='https://api.twitter.com/oauth/request_token',
                         accessURL='https://api.twitter.com/oauth/access_token',
                         authURL= 'https://api.twitter.com/oauth/authorize')

save(cred, file="twitter_authentication.Rdata")

cred$handshake()
#WAIT and authorize your application API key

registerTwitterOAuth(cred)

tweets <- searchTwitter("@Walmart",n=200, lang="en", since='2014-12-04', until='2014-12-05')

length(tweets)

tweets.id <- sapply(tweets, function(x) x$getId())
tweets.text <- sapply(tweets, function(x) x$getText())
tweets.screenname <- sapply(tweets, function(x) x$getScreenName())
tweets.isretweet <- sapply(tweets, function(x) x$getIsRetweet())
tweets.retweeted <- sapply(tweets, function(x) x$getRetweeted())
tweets.created <- sapply(tweets, function(x) x$getCreated())

head(tweets.text)

df <- data.frame(tweets.id, tweets.text, tweets.screenname, tweets.isretweet, tweets.retweeted, tweets.created)
names(df) <-c("id", "text", "screenname", "isretweet", "retweeted", "created")
write.table(df, file = "walmart4.txt", append = TRUE)

pos <- scan("positive-words.txt",what="character",comment.char=";")
neg <- scan("negative-words.txt",what="character",comment.char=";")

tweets.corpus <- Corpus(VectorSource(tweets.text))

tweets.corpus <- tm_map(tweets.corpus, tolower) 
tweets.corpus <- tm_map(tweets.corpus, removePunctuation)
tweets.corpus <- tm_map(tweets.corpus, function(x) removeWords(x,stopwords()))

corpus.split <- lapply(tweets.corpus,strsplit,"\\s+")

matches <- lapply(corpus.split,function(x) {
  match.pos <- match(x[[1]],pos)
  match.neg <- match(x[[1]],neg) 
  
  
  list(length(which(!is.na(match.pos))),length(which(!is.na(match.neg))))
})

match.matrix <- matrix(unlist(matches),nrow=length(matches),ncol=2,byrow=T)

simple.sentiment <- match.matrix[,1] - match.matrix[,2]

hist(simple.sentiment)

sum(simple.sentiment)

```

Following graph shows comparision of sentiments to actual change in stock price of Walmart.

```{r fig.width=7, fig.height=6}
#Create your CSV Data file out of sentiment analysis and actual data from
#Read this data
WalmartData <- read.csv(file = "Walmart.csv")

WalmartData$Start <- NULL
WalmartData$End <- NULL

WalmartData

WalmartData$Stock.Price <- NULL
WalmartData$Sentiment.Score <- NULL

molten.WalmartData <- melt(WalmartData, id.vars = c("Day", "Tweets"), 
                           measure.vars = c("Sentiment.Prediction", "Actual"))

ggplot(data = molten.WalmartData, aes(x = Day, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("Walmart Stock Sentiment Analysis") +
  scale_fill_manual(values=c("blue", "red"))
```

Summary
We collected data sentiment data from twitter and compared it with actual data which. Sentiments holds true for 60% of time which is 3/5 days we made this analysis. December 1st, 2014 first day and December 3rd, 2014 third day twitter sentiment came out to be wrong for actual stock price. Thus twiter data can't provide with exact prediction of Walmart stock prices.   