UPS
========================================================

This is Twitter sentiment analysis for UPS.

```{r message=FALSE}
library("twitteR")
library("wordcloud")
library("tm")
library("ggplot2")
library("reshape2")
```
Following code was executed & evaluated for five consecutive open market days from December 1st to December 3rd 2014 for twitter UPS.
```{r eval=FALSE}
my.key <-"d93dUzXPNtxT3XLmrBTPDRcyZ"
my.secret <-"A9JijB1Ffdl1Lv98fo1bCihWJgsTXnpmOzsaXa35fl9YssEnHd"

cred <- OAuthFactory$new(consumerKey=my.key,
                         consumerSecret=my.secret,
                         requestURL='https://api.twitter.com/oauth/request_token',
                         accessURL='https://api.twitter.com/oauth/access_token',
                         authURL= 'https://api.twitter.com/oauth/authorize')

save(cred, file="twitter_authentication.Rdata")

cred$handshake()

registerTwitterOAuth(cred)

tweets <- searchTwitter("@UPS",n=200, lang="en", since='2014-11-25', until='2014-11-26')

length(tweets)

tweets.id <- sapply(tweets, function(x) x$getId())
tweets.text <- sapply(tweets, function(x) x$getText())
tweets.screenname <- sapply(tweets, function(x) x$getScreenName())
tweets.isretweet <- sapply(tweets, function(x) x$getIsRetweet())
tweets.retweeted <- sapply(tweets, function(x) x$getRetweeted())
tweets.created <- sapply(tweets, function(x) x$getCreated())

head(tweets.text)

df <- data.frame(tweets.id, tweets.text, tweets.screenname, tweets.isretweet, tweets.retweeted, tweets.created)
names(df) <-c("id", "text", "screenname", "isretweet", "retweeted", "created")
write.table(df, file = "ups.txt", append = TRUE)

pos <- scan("positive-words.txt",what="character",comment.char=";")
neg <- scan("negative-words.txt",what="character",comment.char=";")

tweets.corpus <- Corpus(VectorSource(tweets.text))

tweets.corpus <- tm_map(tweets.corpus, tolower) 
tweets.corpus <- tm_map(tweets.corpus, removePunctuation)
tweets.corpus <- tm_map(tweets.corpus, function(x) removeWords(x,stopwords()))

corpus.split <- lapply(tweets.corpus,strsplit,"\\s+")

matches <- lapply(corpus.split,function(x) {
  match.pos <- match(x[[1]],pos)
  match.neg <- match(x[[1]],neg) 
  
  
  list(length(which(!is.na(match.pos))),length(which(!is.na(match.neg))))
})

match.matrix <- matrix(unlist(matches),nrow=length(matches),ncol=2,byrow=T)

simple.sentiment <- match.matrix[,1] - match.matrix[,2]

hist(simple.sentiment)

sum(simple.sentiment)
```

Following graph shows comparision of sentiments to actual change in stock price of UPS.

```{r fig.width=7, fig.height=6}
#Create your CSV Data file out of sentiment analysis and actual data from
#Read this data
df <-read.csv(file="UPSDATA.csv")

upsdata <- read.csv(file = "UPSDATA.csv")

upsdata$Start <- NULL
upsdata$End <- NULL
upsdata
upsdata$Stock.Price <- NULL
upsdata$Sentiment.Score <- NULL

molten.upsdata <- melt(upsdata, id.vars = c("Day", "Tweets"), 
                          measure.vars = c("Sentiment.Prediction", "Actual"))

ggplot(data = molten.upsdata, aes(x = Day, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = position_dodge()) + 
  ggtitle("UPS Stock Sentiment Analysis") +
  scale_fill_manual(values=c("blue", "red"))


```

Summary
We collected data sentiment data from twitter and compared it with actual data which. Sentiments analysis holds true for 3/5 of times that is from December 1st, 2014 to December 5rd, 2014 out of which 1st, 2nd and 5th day predictions holds true. This doesn't show us a good probability of predicting a company's future stock price. Thus twiter data is not reliable for UPS stock prices. 